On Secure Delegation of SampBQP with a Classical Client

### 2020-01-18 qpip.tex
Add parallel rep ref
Split protocol into two sections

@@

We then extend our scheme for $\QPIP_0$ using results from \cite{mahadev_delegation}.

\subsection{Protocol for Hybrid Client}

@@

\subsection{Protocol for Fully Classical Client}

Here we combine \autoref{QPIP1thm} with results from \cite{mahadev_delegation} to create a delegation protocol for $\SampBQP$ for fully classical clients.

We first restate the construction in \cite{mahadev_delegation}.

Let $\rho$ be an $n$-qubit state. Let $h$ be an n-bits string called the \emph{basis choice}. That is, $h_i=0$ indicates that the $i$-th qubit of $\rho$ is to be measured in the standard basis, while $i=1$ indicates Hadamard basis measurement instead. Let $D_{\rho, h}$ be the distribution of the corresponding measurement results.

\begin{theorem}
    \label{Mahadev_QPIP0_Protocol_Interface}
	Under the assumption that the learning with errors problem with superpolynomial noise ratio is computationally intractable for an efficient quantum machine, there exists a $\QPIP_0$ protocol $(\bbV, \bbP)$ with the following properties:
	\begin{itemize}
	    \item The protocol runs either a ``Hadamard round" or a ``test round" with probability $\fot$ each.
	    \item With a test round, the verifier outputs nothing other than accept/reject
	    \item With a Hadamard round, for prover $\bbP'$, the verifier also obtains a sample from $D_{\bbP', h}$. We define $D^C_{\bbP', h}$ as that distribution conditioned on acceptance.
	    \item (completeness) $\forall n\in\mathcal{B}^{\otimes n}, h\in\bbN$ and $h$, there is a prover with negligible reject probability. Furthermore, $D^C_{\bbP, h}$ has negligible total variation distance to $D_\rho, h$
	    \item (soundness) Fix $\bbP'$ and $h$. Let $p_{h, H}$ be its rejection probability under a Hadamard round, and $p_{h, T}$ be its rejection probability under a test round. Then $\exists\tilde\bbP$ s.t. $\norm{D^C_{\bbP', h} - D_{\tilde\bbP, h}}\leq p_{h,H} + \sqrt{p_{h, T}}+\mu$ for some negligible $\mu$, and $\exists\rho$ s.t. $D_{\tilde\bbP, h}$ is computationally indistinguishable from $D_{\rho, h}$.
	\end{itemize}
\end{theorem}

\Ethan{Maybe wrap the below into a protocol?}

Let $\varepsilon>0$. Pick $N$ large enough so that by

We pick $h$ the same way as we'd decide the measurement basis as in \Ethan{TODO ref protocol 2}.

\Ethan{TODO analyze that the above actually works?}

>>>>

\section{Delegation Protocol for Hybrid Client}

@@

@@
